Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
passive to active

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design models
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
profiles are in good agreement. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Faerenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because axial
conduction was neglected in the \gls{MSRE} design model \cite[p. 99]{briggs_molten-salt_1964}.

@@

\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
Moltres and the \gls{ORNL} \gls{MSRE} design model. Note that the radius for the
plots are chosen to correspond to the peak of the thermal flux in both cases;
for the \gls{ORNL} calculations this is 8.4 inches from the core center-line
because of the effect of the control rod thimbles and extra fuel along the
center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
calculations include the lower and upper plena which are not included in this
report's Moltres model. Consequently, the plot in \cref{fig:msre_axial_fluxes}
extends to lower and higher z-values than
\cref{fig:moltres_axial_fluxes}. Additionally, the deviation of the thermal flux
from a sinusoidal shape in \cref{fig:msre_axial_fluxes} is due to absorption in
the plena.

>>>>

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design models
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
profiles are in good agreement. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Faerenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because axial the \gls{MSRE} design model 
neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.

@@

\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
Moltres and the \gls{ORNL} \gls{MSRE} design model. Note that the radius for the
plots are chosen to correspond to the peak of the thermal flux in both cases;
for the \gls{ORNL} calculations this is 8.4 inches from the core center-line
because of the effect of the control rod thimbles and extra fuel along the
center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
calculations include the lower and upper plena which are not included in this
report's Moltres model. Consequently, the plot in \cref{fig:msre_axial_fluxes}
extends to lower and higher z-values than
\cref{fig:moltres_axial_fluxes}. Additionally, absorption in the plena caused 
deviation of the thermal flux from a sinusoidal shape in 
\cref{fig:msre_axial_fluxes}.
